Towards typed repositories of proofs \\[0.6em] \small \textsf{MIPS 2010}

### 2010-07-06 talks/MIPS2010/slides.tex
Git inspiration...
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@142 403e655e-980a-47bd-8c60-1ee5348bb6b7

More precisely, here are some problems that arise with the traditional
tools when editing proofs. Whereas the usual edit, compile, commit
loop may be a satisfactory approximation when developing software, the
additional demands of proof-checking makes it unsatisfactory as the
development grows: often the time of recompilation is prohibitive.

@@

\begin{frame}{The impact of changes}
  \vspace{0.5em}
  \begin{center}
    \only<1-3>{\includegraphics[width=0.75\textwidth]{images/coqide.png}}%
    \only<4>{\includegraphics[width=0.75\textwidth]{images/coqide2.png}}%
    \only<5>{\includegraphics[width=0.75\textwidth]{images/coqide4.png}}%
    \only<6>{\includegraphics[width=0.75\textwidth]{images/coqide5.png}}%
    \only<7>{\includegraphics[width=0.75\textwidth]{images/coqide6.png}}%
    \only<8>{\includegraphics[width=0.75\textwidth]{images/coqide7.png}}%
  \end{center}
  \pause
  \uncover<2->{
    \begin{itemize}
    \item File-based separate compilation
      \pause
    \item Interaction loop with global undo
    \end{itemize}
  }
\end{frame}

@@

\begin{frame}{Inspiration: the \textsf{git} storage model}
  \begin{itemize}
  \item ``Content-adressable''
  \item Name reflects content
  \item Maximal sharing (or hashconsing)
  \end{itemize}

  Let's design a \emph{typed} \textsf{git} to do incremental type-checking
\end{frame}

>>>>

More precisely, here are some problems that arise with the traditional
tools when editing proofs. Whereas the usual edit, compile, commit
loop may be a satisfactory approximation when developing software, the
extra computational cost of proof-checking makes it unsatisfactory as
the development grows: often the time of recompilation is prohibitive.

@@

\begin{frame}{The impact of changes}
  \vspace{0.5em}
  \begin{center}
    \only<1>{\includegraphics[width=0.75\textwidth]{images/coqide00.png}}%
    \only<2>{\includegraphics[width=0.75\textwidth]{images/coqide0.png}}%
    \only<3>{\includegraphics[width=0.75\textwidth]{images/coqide.png}}%
    \only<4>{\includegraphics[width=0.75\textwidth]{images/coqide2.png}}%
    \only<5>{\includegraphics[width=0.75\textwidth]{images/coqide4.png}}%
    \only<6>{\includegraphics[width=0.75\textwidth]{images/coqide5.png}}%
    \only<7>{\includegraphics[width=0.75\textwidth]{images/coqide6.png}}%
    \only<8>{\includegraphics[width=0.75\textwidth]{images/coqide7.png}}%
  \end{center}
  \pause
  \uncover<2->{
    \begin{itemize}
    \item File-based separate compilation
      \pause
    \item Interaction loop with global undo
    \end{itemize}
  }
\end{frame}

@@

\begin{frame}{Inspiration: the \textsf{git} storage model}
  \begin{center}
    \begin{overlayarea}{\textwidth}{12em}
      \only<2>{\includegraphics[width=0.85\textwidth]{images/git1.pdf}}%
      \only<3>{\includegraphics[width=0.85\textwidth]{images/git2.pdf}}%
      \only<4>{\includegraphics[width=0.85\textwidth]{images/git3.pdf}}%
      \only<5>{\includegraphics[width=0.85\textwidth]{images/git4.pdf}}%
      \only<6-9>{\includegraphics[width=0.85\textwidth]{images/git5.pdf}}%
      \only<10>{
        \begin{center}
          \vspace{5em}
          {\Large Let's design a \emph{typed} \textsf{git}}
        \end{center}
      }%
    \end{overlayarea}
  \end{center}%
  \begin{itemize}\small %
  \item<7-> ``Content-adressable''%
  \item<8-> Name reflects content%
  \item<9-> Maximal sharing (or hash-consing)%
  \end{itemize}%
\end{frame}

\textsf{Git} is one of the most successful version control system, and
part of its success is due to the very simple, yet very efficient
storage model. It doesn't keep track of changes \emph{per se}, but of
similarities between version. Given a base directory structure,
already committed in its database, and a new version of it with, let's
say, one file changed -- \texttt{f3.txt}, it stores the new version by
linking all common subdirectory structure to the previous version.
This is possible because every node in the tree, directories and
files, have a unique name. So actually, the database of \textsf{git}
looks like this.

Moreover, similarities are easily tracked because every name is
carefully chosen to reflect the \emph{content} of a file or directory.
In practice, \texttt{git} uses a hash function to produce all names in
the database: files are given the hash of their content, and
directories are given the hash of the hash of all the files it
contains, recursively.

This way, we ensure that no two subdirectories with different content
appear in the database, that is, we enforce maximal sharing among
subdirectories. In functional programming, this is called
hash-consing.
